\normalfont{A statistical analysis on factors that contributed/slowed down the spread of COVID-19}

### 2020-09-07 Manuscript/Manuscript.tex
pub

>>>>

Looking to the figure \ref{Regions_CorrMatrix},as for the provinces also in this case we found a positive correlation between the Mean Income and the Cases. Furthermore here, since the overall number of tests are available as well as the number of deaths for COVID19, we see that these two normalized quantities are positively correlated with the cases. The causal connection for these three quantities is simple: in order to validate that a patient is infected a test is required, and a part of the infected patient are going to die for COVID19 \footnote{Note that the worst pandemic in human history in terms of deaths, the Spanish Flu (1918-1920), had a mortality ratio that was near 2.5 $\%$ \cite{zimmer2009historical}, so the \textit{small} percentages must be considered carefully}. The correlation matrix also highlights that there is a positive correlation between the number of people for general practitioner and the number of cases; moreover a higher number of normalized visit is negatively correlated with the number of cases and the mortality.
